MCMC Redistricting

### 2020-12-13 paper.Rmd
results update

There seems to be a connection between political bias and percentage of precincts swapped. When less than 10 percent of precincts are swapped the political bias changes very little and stays democratic but it can sway slightly closer to the ideal 0 bias line. However as more precincts get swapped we start to see a positive trend in the graph where partisan bias grows more and more in favor of democrats. According to our simulations in order to acheive 0 bias approximately 37 percent of precincts need to be swapped from their original district. The political bias can even become slightly republican with this proportion of precincts swapped. However, the over all trend is that the vast meajority of the simulations that were run return a district map of colorado that is even more democratically biased than it currently is. This could be due to the fact that Colorado has been trending away from being a swing state and becoming more of a solid "blue" state over the past 20 or so years.

@@

>>>>

There seems to be a connection between political bias and percentage of precincts swapped. When less than 10 percent of precincts are swapped the political bias changes very little and stays democratic but it can sway slightly closer to the ideal 0 bias line. However as more precincts get swapped we start to see a positive trend in the graph where partisan bias grows more and more in favor of democrats. According to our simulations in order to acheive 0 bias approximately 37 percent of precincts need to be swapped from their original district. The political bias can even become slightly republican with this proportion of precincts swapped. However, the over all trend is that the vast meajority of the simulations that were run return a district map of colorado that is even more democratically biased than it currently is. We believe this is due to the fact that Colorado has been trending away from being a swing state and becoming more of a solid "blue" shown by the outcomes of the presedential elections in the past 20 years.

@@

Here is the minimum bias map. This map shows the simulation with the political bias that is closest to 0. This map does satisfy all of the constraints put forth by the state of colorado for redistricting however it may be slightly unrealistic as far as a real world district map. The districts developed a "tree branch pattern" where they seem to branch out accross the entire state of colorado from the center outwards. This is because of a compactness constraint that we were not able to implement due to our limited computing power. The compactness constraint takes in a matrix of pair wise distances between precincts and makes sure that all precincts in a district are not "too" far away from eachother. We tried running our simulations using this constraint but it crashed our computers so we decided to run or simulations without compactness. However we think there is something to be learned from this minimum bias map, it shows just how different districts need to look in Colorado to obtain a 0 bias state.
